Compositional Equivalences Based on Open pNets

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
RW organisation

\ERIC{Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
}

@@

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
\ERIC{This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}. Our approach is semantical and more global: our sufficient condition applies to a whole (open) system, and is expressed on its open automaton (see Definition \ref{def:non-obspNet}).}
%\TODO{Eric: relations with SOS rule formats?}

@@

\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems. The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.  }

\RAB{
PNets have features of "known" compositional specification theory  allowing for modular and possibly incomplete  description   and  structural compositions \cite{HuttelL89,Larsen:91} of systems.}

@@

@@

>>>>

Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.

@@

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}. Our approach is semantical and more global: our sufficient condition applies to all the synchronisations at a given composition level of an (open) system and not on individual rules. It is expressed on the open automaton (see Definition \ref{def:non-obspNet}).
%\TODO{Eric: relations with SOS rule formats?}

@@

@@

In the same vein as  context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems. The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.  
PNets have similar features as context systems \cite{Larsen:91} and static constructs \cite{HuttelL89}. Indeed all these approaches allow for modular and possibly incomplete  description   and  structural composition of systems. The main originality of pNets  compared to these other compositional approaches is the parameterised nature of the specification, which enables reasoning on value-passing systems but also on rich synchronisations that depend on the value of parameters.

\subsubsection*{Decomposition techniques}

@@

\subsubsection*{Logical and semantics approaches}
